Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions

### 2024-01-14 paper/arxiv/main_4.2_volcano_plots.tex
format fixes
fix caption text

\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{main_fig3_volcano.png}
    \caption{\textbf{Limiting Potential Volcano Plot and Periodic Table.}}
    a. Limiting potential volcano plot computed from hybrid-descriptor-based linear scaling relations at -0.17 V vs SHE.
    In the plot, the circle, triangle, square, diamond, plus, and star symbols represent metals supported on g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, BN, and C\textsubscript{2}N, respectively.
    Dotted purple lines delineate regions representing rate-determining steps (RDS), with roman numerals denoting the respective RDS for each region.
    b. Limiting potential periodic table illustrating the theoretical activity of single atom catalysts, where metals are supported on g-C\textsubscript{3}N\textsubscript{4}.
    \label{main_fig3:volcano}
\end{figure}

>>>>

% Figure 3: Limiting Potential Volcano Plot and Periodic Table
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{main_fig3_volcano.png}
    \caption{\textbf{Limiting Potential Volcano Plot and Periodic Table.}
    a. Limiting potential volcano plot computed from hybrid-descriptor-based linear scaling relations at -0.17 V vs SHE.
    In the plot, the circle, triangle, square, diamond, plus, and star symbols represent metals supported on g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, BN, and C\textsubscript{2}N, respectively.
    Dotted purple lines delineate regions representing rate-determining steps (RDS), with roman numerals denoting the respective RDS for each region.
    b. Limiting potential periodic table illustrating the theoretical activity of single atom catalysts, where metals are supported on g-C\textsubscript{3}N\textsubscript{4}.}
    \label{main_fig3:volcano}
\end{figure}
